---
title: "FinalProjTeam6"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  markdown: 
    wrap: 72
---

2.  決定題目的方向:

-   觀測對象與想要探索的現象 (關係)

3.  基本資料分析 (資料視覺化) 在大數據的時代,
    資料的整理與有意義訊息的呈現 (畫圖製表)越來越重要.
4.  加入統計的思維進行進一步分析

<!-- -->

a.  思考(轉換後)變數的角色

-   若想要建立模型, 區別response or explanatory variables
-   response 可以不只一個
-   模型亦可以有多個 (最後比較或進行選模)
-   亦可以不區別變數角色, 單純的探討關聯性

b.  套用統計方法時要先判斷變數型態 ("連續" 或是 "類別資料")

-   蒐集到資料以後, 也有可能把連續變數以類別變數重新編碼
    例如連續的年齡可以分類為 "青年" "中年" "老年"\

c.  思考觀測值之個數 (樣本數)

-   個數太少可能結果 "不顯著"

d.  設計抽樣或是實驗方法
e.  先對感興趣之關係做初步猜測 (建立假設)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
cervical_cancer <- read.csv("cervical_cancer.csv", na.strings = "?")
cervical_cancer
```

## Data Preview

```{r}
summary(cervical_cancer)
```

Comments: To answer the question "Is the distribution of data attached
to the real-word scenario?", we could infer from the data that: The
people who got cervical cancer (Dx.Cancer == 1) is 18 by the total data
count(858 datas) and the mean of column.

### Plot the distribution

```{r}
library(ggplot2)

for (col in names(cervical_cancer)) {
  if (is.numeric(cervical_cancer[[col]])) {
    p <- ggplot(cervical_cancer, aes(x = !!sym(col))) +
      geom_histogram()
    print(p)
  }
}
```

Assumption: If the individual get sex in their early age
(First.sexual.intercourse) , then they might have higher chance to get
cervical cancer (Dx.Cancer)

### Logistics predict Dx.cancer by First.sexual.intercourse

```{r}
model <- glm(Dx.Cancer ~ First.sexual.intercourse, data = cervical_cancer, family = binomial)
summary(model)
```

Comments: The model suggests that the age of first sexual intercourse
(**`First.sexual.intercourse`**) has a statistically significant effect
on the likelihood of having cervical cancer (**`Dx.Cancer`**). However,
the relationship is relatively weak since the p-value (0.0524) is failed
to reject the threshold of 0.05.

TODO:

1\. Plot the files\
2. See Correlation\
3. 像多少比例得病這種問題要答的出來（索取樣的對象是否為一般的『大眾』）

## Full model logistic regression + stepAIC to get a smaller model

```{r}
library(MASS)

# Remove the specified features from the dataset
cervical_cancer <- cervical_cancer[, !(names(cervical_cancer) %in% c("STDs..Time.since.first.diagnosis", "STDs..Time.since.last.diagnosis", "STDs.AIDS", "STDs.cervical.condylomatosis"))]

# Remove rows with missing values from the dataset
cervical_cancer_clean <- na.omit(cervical_cancer)

```

### Get \`Cervical_cancer_clean\` done

```{r}

# Fit a full logistic regression model using the cleaned dataset
full_model <- glm(Dx.Cancer ~ ., data = cervical_cancer_clean, family = binomial)

# Perform stepAIC with backward method
step_model <- stepAIC(full_model, direction = "backward")

# Print the summary of the step_model
summary(step_model)
```

## StepAIC model Fitted result

View the summary of last fitted

**The results are: Smokes + Smokes..years. + Dx.CIN + Dx.HPV + Dx**

```{r}
res = glm(formula = Dx.Cancer ~ Smokes + Smokes..years. + Dx.CIN + 
    Dx.HPV + Dx, family = binomial, data = cervical_cancer_clean)
summary(res)
```

```{r}
library(MASS)

library(caTools)
set.seed(123)
split <- sample.split(cervical_cancer_clean$Dx.Cancer, SplitRatio = 0.7)
train <- cervical_cancer_clean[split, ]
test <- cervical_cancer_clean[!split, ]

# Train by logistic regression
logistic_model <- glm(Dx.Cancer ~ ., data = train, family = binomial)

# Test the data and show the confusion matrix
library(caret)
predicted <- predict(logistic_model, newdata = test, type = "response", na.action = na.pass)
predicted <- ifelse(predicted > 0.5, 1, 0)
predicted[is.na(predicted)] <- 0
predicted <- factor(predicted, levels = c(0, 1))
test$Dx.Cancer <- factor(test$Dx.Cancer, levels = c(0, 1))

confusionMatrix(predicted, test$Dx.Cancer)

# with(summary(res), 1-deviance/null.deviance)
```

## Doing T test first to select important feature then do backward selection

Full model then do StepAIC may contains features that's not significant
enough.

**Filter w/ t-test then do StepAIC again.**

```{r}
# Split the data into two groups: with and without cervical cancer
with_cancer <- cervical_cancer[cervical_cancer$Dx.Cancer == 1, ]
without_cancer <- cervical_cancer[cervical_cancer$Dx.Cancer == 0, ]
ignore = list("STDs..Time.since.first.diagnosis", "STDs..Time.since.last.diagnosis", "Dx.Cancer")
significant_features <- list()
# Loop through the columns and perform t-tests for numeric features
for (col in names(cervical_cancer)) {
  # print(col)
  if (col %in% ignore) next
  if (is.numeric(cervical_cancer[[col]])) {
    t_test_result <- t.test(with_cancer[[col]], without_cancer[[col]], na.rm = TRUE)
#    cat(col, "t-test result:\n")
#    print(t_test_result)
#    cat("\n")
#    print(t_test_result$p.value < 0.05)
    # Some value that is too small cannot compare may lead to NA    
    if (is.na(t_test_result$p.value < 0.05) ||  t_test_result$p.value < 0.05) {
      cat(col, "t-test result:\n")
      print(t_test_result)
      cat("\n")
      significant_features <- append(significant_features, col)
    }
  }
}
print(significant_features)
```

## ANOVA after T-test

```{r}
# print(significant_features)
# library(car)

# Create a formula for the F-test using the significant features
f_test_formula <- as.formula(paste("Dx.Cancer ~", paste(significant_features, collapse = " + ")))

# Fit a linear model using the formula
f_test_model <- lm(f_test_formula, data = cervical_cancer)

# Perform the F-test
f_test_result <- anova(f_test_model)

# Print the F-test result
print(f_test_result)
```

### Logistic regression test by StepAIC after significant-T

```{r}
library(MASS)

# Create a formula for the stepAIC using the significant features
stepAIC_formula <- as.formula(paste("Dx.Cancer ~", paste(significant_features, collapse = " + ")))

# Fit a logistic regression model using the formula
stepAIC_model <- glm(stepAIC_formula, data = cervical_cancer, family = binomial)

# Remove rows with missing values from the dataset
cervical_cancer_clean <- na.omit(cervical_cancer)

# Split the dataset into training set and testing set
library(caTools)
set.seed(123)
split <- sample.split(cervical_cancer_clean$Dx.Cancer, SplitRatio = 0.7)
train <- cervical_cancer_clean[split, ]
test <- cervical_cancer_clean[!split, ]
# Fit a logistic regression model using the formula and cleaned dataset
stepAIC_model <- glm(stepAIC_formula, data = train, family = binomial)

stepAIC_result <- stepAIC(stepAIC_model, direction = "backward")
# Print the stepAIC result
print(stepAIC_result)

```

```{r}
summary(train)
```

```{r}

library(MASS)

# Remove the specified features from the dataset
cervical_cancer <- cervical_cancer[, !(names(cervical_cancer) %in% c("STDs..Time.since.first.diagnosis", "STDs..Time.since.last.diagnosis", "STDs.AIDS", "STDs.cervical.condylomatosis"))]

# Remove rows with missing values from the dataset
cervical_cancer_clean <- na.omit(cervical_cancer)

# Test the data and show the confusion matrix
library(caret)
predicted <- predict(stepAIC_model, newdata = test, type = "response")
predicted <- ifelse(predicted > 0.5, 1, 0)

# Replace NA in predicted to 0
predicted[is.na(predicted)] <- 0
predicted <- factor(predicted, levels = c(0, 1))
test$Dx.Cancer <- factor(test$Dx.Cancer, levels = c(0, 1))

confusionMatrix(predicted, test$Dx.Cancer)
```

# **Logistic regression in R with rare event data**

```{r}
library(logistf)
fit2<-logistf(data=cervical_cancer_clean, Dx.Cancer~Smokes + Smokes..years. + Dx.CIN + Dx.HPV + Dx, first=FALSE, pl=TRUE)
summary(fit2)
exp(coef(fit2))
```

Comment: idunno :)

我真的看不出來這個解釋....看起來是係數大的表現好？

## Two-Way ANOVA （but finally we use brute force）

Separate features those into groups 1-4

Make Some assumptions:

a\. Women w/ IUD (宮內節育器) (Type II) has more chance to get
STDs:pelvic inflammatory disease (STDs:盆腔炎症) (Type III)

```{r}

```

b\. First sexual intercourse (age) (第一次性交(年齡)) (Type II ) in a
younger age, more chances to get Cancer (Type IV)

Hint: some other diseases may also concern w/ First sexual intercourse

c\. 假設擁有較多性病的女性擁有子宮頸癌的機率較高 \<Compilcated\>

d\. 假設年齡越大擁有子宮頸癌的機率較高

e\. Brute force (Type IV) \~ (Type II) \* (Type III)

```{r}
names(cervical_cancer)
```

```{r}
# Check factors with less than 2 levels
dataset <- cervical_cancer # Replace 'cervical_cancer' with the actual name of your dataset

# Get the column names of factors with less than 2 levels
factors_with_less_than_2_levels <- names(dataset)[sapply(dataset, function(x) is.factor(x) && length(levels(x)) < 2)]

# Print the factors with less than 2 levels
cat("Factors with less than 2 levels:\n")
cat(paste(factors_with_less_than_2_levels, collapse = ", "))

```

```{r}
model <- aov(Dx.Cancer ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)
```

#### This is useless

```{r}
cervical_cancer$Dx.Cancer <- factor(cervical_cancer$Dx.Cancer, levels = c(0, 1))
cervical_cancer$Dx.CIN <- factor(cervical_cancer$Dx.CIN, levels = c(0, 1))
cervical_cancer$Dx.HPV <- factor(cervical_cancer$Dx.HPV, levels = c(0, 1))
cervical_cancer$Dx <- factor(cervical_cancer$Dx, levels = c(0, 1))
cervical_cancer$Hinselmann <- factor(cervical_cancer$Hinselmann, levels = c(0, 1))
cervical_cancer$Schiller <- factor(cervical_cancer$Schiller, levels = c(0, 1))
cervical_cancer$Citology <- factor(cervical_cancer$Citology, levels = c(0, 1))
cervical_cancer$Biopsy <- factor(cervical_cancer$Biopsy, levels = c(0, 1))

TYPE_I = c("Age", "Number.of.sexual.partners", "Num.of.pregnancies")
TYPE_II = c("First.sexual.intercourse", "Smokes", "Smokes..years.", "Hormonal.Contraceptives", "Hormonal.Contraceptives..years.", "IUD", "IUD..years.")
TYPE_III = c("STDs..number.", "STDs.condylomatosis", "STDs.syphilis", "STDs.pelvic.inflammatory.disease", "STDs.genital.herpes", "STDs.molluscum.contagiosum", "STDs.AIDS", "STDs.HIV", "STDs.Hepatitis.B", "STDs.HPV", "STDs..Number.of.diagnosis")
TYPE_IV = c("Dx.Cancer", "Dx.CIN", "Dx.HPV", "Hinselmann", "Schiller", "Citology", "Biopsy")

for (IV in TYPE_IV) {
  for (II in TYPE_II){
    for (III in TYPE_III){
      print(IV)
      print(II)
      print(III)
      model <- try(aov(cervical_cancer[[IV]] ~ cervical_cancer[[II]] * cervical_cancer[[III]], data = cervical_cancer))
      if(class(model) != "try-error"){
        summary(model)
      } else {
        print(paste("Error in model.frame.default(formula = cervical_cancer$", IV, " ~ cervical_cancer$", II, " * cervical_cancer$", III, ":  invalid type (NULL) for variable 'cervical_cancer$", IV, "'", sep = ""))
      }
    }
  }
}
```

```{r}
model <- aov(First.sexual.intercourse ~ Smokes * STDs..number. , data = cervical_cancer)
summary(model)
```

### Draw 2-way anova test graph

```{r}
# Box plot with two factor variables
boxplot(First.sexual.intercourse ~ Smokes * STDs..number., data=cervical_cancer, frame = FALSE, 
        col = c("#00AFBB", "#E7B800"), ylab="First sexual intercourse")
# Two-way interaction plot
interaction.plot(x.factor = cervical_cancer$STDs..number., trace.factor = cervical_cancer$Smokes, 
                 response = cervical_cancer$First.sexual.intercourse, fun = mean, 
                 type = "b", legend = TRUE, 
                 xlab = "STDs..number.", ylab="First sexual intercourse",
                 pch=c(1,19), col = c("#00AFBB", "#E7B800"))
```

## Codegen Brute Force

test this first

```{r}
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)
```

Then do the whole

```{r}
print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.Cancer")
model <- aov( Dx.Cancer ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.CIN")
model <- aov( Dx.CIN ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Dx.HPV")
model <- aov( Dx.HPV ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Hinselmann")
model <- aov( Hinselmann ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Schiller")
model <- aov( Schiller ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Citology")
model <- aov( Citology ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

print("Biopsy")
model <- aov( Biopsy ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)


```

Separately:

Dx.Cancer

```{r}
model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.Cancer ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)
```

Dx.CIN

```{r}

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.CIN ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)
```

Dx.HPV

```{r}

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Dx.HPV ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)
```

Hinselmann

```{r}

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Hinselmann ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)
```

Schiller

```{r}

model <- aov( Schiller ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Schiller ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)
```

Citology

```{r}

model <- aov( Citology ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Citology ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)
```

Biopsy

```{r}

model <- aov( Biopsy ~ First.sexual.intercourse * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ First.sexual.intercourse * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Smokes..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ Hormonal.Contraceptives..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs..number., data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.condylomatosis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.syphilis, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.pelvic.inflammatory.disease, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.genital.herpes, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.molluscum.contagiosum, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.AIDS, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.HIV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.Hepatitis.B, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs.HPV, data = cervical_cancer)
summary(model)

model <- aov( Biopsy ~ IUD..years. * STDs..Number.of.diagnosis, data = cervical_cancer)
summary(model)
```

See log at file Significant.txt
